\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-10 coqimpl.tex
address two comments

An \lsti{FInductive} definition is translated to a parameterized module type.
Consider the inductive type \lsti{tm}.
In \lsti{STLC}, it is translated to a top-level module type
\lsti{STLC\_tm} that declares a \lsti{tm} type,
its constructors (e.g., \lsti{tm_abs}) \EDJ{I am not sure if it is better we emphasize in the following way :`` that declares a tm type, its constructors (e.g. tmabs) as a normal function,.. '' i.e. emphasize it is a normal function in the module type},
its partial recursor (\lsti{tm_prect_STLC}),
and the propositional equalities\EDJ{I propose to change this sentence to ``and the prop eq about computational behaviour on the partial recursor''. And thus in the other parts of the paper, we can use the word ``computational behaviour'' instead of prop eq. Because just saying prop eq seems a bit of lack of context/details.} on the partial recursor
(e.g., \lsti{tm_abs_eq_STLC}; \cref{sec:prec}).

Importantly,
\lsti{STLC\_tm} merely declares the existence of these names and their types;
it does not specify their definitions.
Having these names and their types available through the context parameters (\lsti{self})
suffices for the translations of the subsequent fields to be type-checked by Coq.
Leaving the definitions open enables \lsti{STLC} and \lsti{STLCFix}
to instantiate \lsti{tm} differently upon \lsti{End}~\lsti{STLC} and \lsti{End}~\lsti{STLCFix}.

>>>>

An \lsti{FInductive} definition is translated to a parameterized module type.
Consider the inductive type \lsti{tm}.
In \cref{fig:stlc-compiled}, it is translated to a top-level module type
\lsti{STLC\_tm} that declares a \lsti{tm} type,
four functions standing for the constructors,
%\EDJ{I am not sure if it is better we emphasize in the following way :`` that declares a tm type, its constructors (e.g. tmabs) as a normal function,.. '' i.e. emphasize it is a normal function in the module type},
a partial recursor (\lsti{tm_prect_STLC}),
and the computational behaviors of the partial recursor
(e.g., \lsti{tm_abs_eq_STLC}). %\cref{sec:prec}.
%\EDJ{I propose to change this sentence to ``and the prop eq about computational behaviour on the partial recursor''. And thus in the other parts of the paper, we can use the word ``computational behaviour'' instead of prop eq. Because just saying prop eq seems a bit of lack of context/details.}

Importantly,
\lsti{STLC\_tm} merely declares the existence of these names and their types;
it does not specify their definitions.
Having these names and their types available through the context parameters (\lsti{self})
suffices for the translations of the subsequent fields to be type-checked by Coq.
Leaving the definitions unspecified enables \lsti{STLC} and \lsti{STLCFix}
to instantiate \lsti{tm} differently upon \lsti{End}~\lsti{STLC} and upon \lsti{End}~\lsti{STLCFix}.
